\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-08 main.tex
CM

\xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes}, \textsc{Imdb-Binary}, \textsc{Imdb-Multi}, \textsc{Mcf-7}, \textsc{Molt-4},    \textsc{NCI1}, \textsc{Proteins},
\textsc{Reddit-Binary},    \textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257} graph classification datasets, and the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets. See the website for dataset statistics.

@@

\subsection{Results and discussion}
See~\cref{t2l,t2ll,neural_short_tt}. On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines. However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation. Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall. On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline.

@@

We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data. We believe that our dataset collection will spark further progress in graph representation learning. We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.

>>>>

\xhdr{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes}, \textsc{Imdb-Binary}, \textsc{Imdb-Multi}, \textsc{Mcf-7}, \textsc{Molt-4},    \textsc{NCI1}, \textsc{Proteins},
\textsc{Reddit-Binary},    \textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257} graph classification datasets, and the \textsc{Alchemy}, \textsc{QM9}, \textsc{Zinc} (multi-target) regression datasets. See the website for dataset statistics. We

@@

\subsection{Results and discussion}
\cref{t2l,t2ll,neural_short_tt} summarize the results. On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beaten by the $1$-\textsc{WL} or the neural baselines. However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation. Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall. On the molecular learning tasks, see \cref{neural_short_tt}, it becomes apparent that specialized architecture such as \textsc{MPNN} result in signifcant gains over the generic \textsc{Gin-$\varepsilon$} baseline. For the neural baselines unlike the kernel baselines, we used one-hot degree features for datasets that do not provide node label.

@@

We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data. We believe that our dataset collection will spark further progress in graph representation learning, and that our unified evaluation procedures will lead to more comparable results. We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.
